% A complete, runnable LaTeX document for your resume
\documentclass[10pt, a4paper, sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[a4paper, top=1.5cm, bottom=1.5cm, left=1.8cm, right=1.8cm]{geometry}
\renewcommand{\labelitemi}{\textbullet}

% --- PERSONAL INFORMATION ---
\name{Vishal}{Shaji}
\title{DevOps / Cloud Engineer}

\address{\vspace{2.5mm}Kochi, India}{}
\phone[mobile]{+91 7306997081}
\email{vishshaji03@gmail.com}
\social[linkedin]{VishalShaji}
\social[github]{Vishhh03}

\begin{document}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    pdftitle={Vishal Shaji - DevOps Resume},
}

\makecvtitle
\vspace*{-10mm}

% --- SUMMARY ---
\section{Summary}
DevOps / Cloud Engineer with hands-on experience in AWS, Docker, Kubernetes, CI/CD, and monitoring.
Built and operated cost-efficient, highly available infrastructure with real-world production metrics.

% --- EXPERIENCE ---
\section{Experience}

\cventry
  {July 2025 -- Present}
  {Programmer Analyst Trainee}
  {Cognizant Technology Solutions (CTS)}
  {Chennai, India}
  {}
  {
  \begin{itemize}\setlength{\itemsep}{2pt}
    \item Built and deployed a multi-tier hotel management system using Angular, .NET, and SQL Server following enterprise DevOps workflows.
    \item Containerized applications using Docker and implemented CI/CD pipelines with GitHub Actions for automated build and deployment.
    \item Implemented monitoring and centralized logging using Prometheus, Grafana, and ELK Stack.
    \item Maintained Git workflows and performed pull request reviews to ensure code quality and pipeline stability.
  \end{itemize}}

\vspace{2mm}

\cventry
  {Jan 2025 -- June 2025}
  {Tech Consultant (Intern)}
  {Bommaku Constructions}
  {Hyderabad, India}
  {}
  {
  \begin{itemize}\setlength{\itemsep}{2pt}
    \item Advised management on adopting cloud-based workflows for real-time architectural demos and client presentations.
    \item Designed Unreal Engine 5 architectural visualizations to support technical sales and stakeholder engagement.
  \end{itemize}}

% --- PROJECTS ---
\section{Projects}

\cventry
  {}
  {Cloud DevOps Live Project}
  {TerraLess -- Stateless Server Hosting}
  {}
  {}
  {
  \begin{itemize}\setlength{\itemsep}{2pt}
      \item Built a \textbf{SaaS platform} for self-hosted gaming servers on \textbf{Hetzner Cloud} using Docker and Linux, reducing infrastructure costs by \textbf{90\%}.
      \item Engineered ephemeral storage and snapshot-based backups with \textbf{<0.1s} freeze times and near-zero I/O latency.
      \item Designed disaster recovery workflows achieving a \textbf{Recovery Time Objective (RTO) of <60s}.
      \item Implemented offsite replication with \textbf{Hetzner Storage Box} to achieve \textbf{100\% data redundancy} and high availability.
  \end{itemize}
  \textit{Live Site: \url{https://www.terraless.com}}}

\vspace{2mm}

\cventry
  {}
  {Client Website Deployment}
  {Idha Art Stay}
  {}
  {}
  {
  \begin{itemize}\setlength{\itemsep}{2pt}
    \item Deployed and managed a production client website using Next.js, Sanity CMS, GitHub Actions, and Cloudflare CDN.
    \item Implemented CI/CD pipelines, DNS configuration, and SEO optimization for reliable global delivery.
  \end{itemize}
  \textit{Live Site: \url{https://www.idhafortkochi.com}}}

% --- EDUCATION ---
\section{Education}

\cventry
  {2019 -- 2023}
  {Bachelor of Technology (B.Tech) -- Civil Engineering \\ \small Minor in Machine Learning}
  {TOCH Institute of Science and Technology}
  {Kochi, India}
  {}
  {
  \begin{itemize}
    \item Led a machine learning-based data analysis project focused on Kochi Metro network analytics.
  \end{itemize}}

\cventry
  {2017 -- 2019}
  {Higher Secondary Education -- Computer Science}
  {Gregorian Public School}
  {Kochi, India}
  {}
  {}

% --- TECHNICAL SKILLS ---
\section{Technical Skills}

\cvitem{DevOps \& Cloud}{AWS (EC2, Lambda, IAM, S3, CloudWatch, ECS, SNS, Cognito), Docker, Kubernetes, Terraform, GitHub Actions, Prometheus, Grafana, ELK Stack, Bash, Git}
\cvitem{Programming}{Python, JavaScript, C\#, SQL}
\cvitem{Web \& APIs}{Angular, .NET Core, Next.js, React, FastAPI, Headless CMS}
\cvitem{Databases}{PostgreSQL, SQL Server, DynamoDB, MongoDB, RDS}
\cvitem{Operating Systems}{Linux (Ubuntu, Amazon Linux)}

% --- CERTIFICATIONS ---
\section{Certifications}

\cvitem{}{AWS Certified Cloud Practitioner}
\cvitem{}{AWS Certified AI Practitioner}
\cvitem{}{Oracle Cloud Infrastructure (OCI) Associate Architect}
\cvitem{}{Oracle Cloud Infrastructure (OCI) Foundational Associate}
\cvitem{}{Oracle Cloud Infrastructure (OCI) Foundational AI}

\end{document}
